Box 1 - TDT Curves

### 2023-09-22 ms/ms.qmd
trying to fix figure

@@

rerun = FALSE
if(rerun){
  pdf(height = 10.2, width = 8.1, file = here::here("output", "fig", "fig1.pdf"))
  layout(mat = layout.matrix) 
  # Plot 1
  plot(t, type = "tidy", cex = 0.65)

>>>>

rerun = FALSE
if(rerun){

@@

  pdf(height = 10.2, width = 8.1, file = here::here("output", "fig", "fig1.pdf"))
  layout(mat = layout.matrix) 
  # Plot 1
  plot(t, type = "tidy", cex = 0.65)
